Draft of paper

### 2024-12-12 Paper draft/draft.tex
Theorem proof ended

\address[First]{Università di Trento, Trento, Italy (e-mail: marco.sterlini@studenti.unitn.it) }
\address[Second]{LAAS-CNRS, Université de Toulouse, CNRS, Toulouse, France (e-mail:bu) }

@@

We can express now the new inter-dependency between the variables of interest:
\begin{equation}\label{eqn:incremental}
  \begin{aligned}
    \tilde{u} &= R_{\omega} \tilde{x} - N_{u \omega} R \tilde{\psi}\\
    \tilde{\nu} &= R N_{\nu x} \tilde{x} + (\Id - R) \tilde{\psi}
  \end{aligned}
\end{equation}

@@

\begin{lemma}\label{lem:finsler}: \emph{Considering the triggering policy \eqref{eqn:dynamic_trig}, $R^i$ such that ${\xi^i}\tr = \!R^i \bmx{\tilde{x} & \tilde{\psi} & \tilde{\nu}}\tr\! = R^i \xi\tr$, with reference to the structure in \eqref{eqn:sec_cond} and assuming \eqref{eqn:incremental} holds for some $\underline{\xi}, \bar{\xi} \in \RR^{n_x + 2n_{\phi}}$ such that $\forall \xi \in \left[ \underline{\xi}, \bar{\xi}\right]$, if $\exists X^i \in\! \RR^{(nx + 2n_{\phi_i}) \times (nx + 2n_{\phi_i})},$ $N^i_1 \in \RR^{n_x \times n_{\phi_i}}, N^i_2, N^i_3 \in \RR^{n_{\phi_i} \times n_{\phi_i}}$ a diagonal matrix $T^i > 0 \in \RR^{n_{\phi_i} \times n_{\phi_i}}, G^i \in \RR^{n_{\phi_i} \times n_x}$ such that:
\begin{equation}\label{eqn:finsler}
     {R^i}\tr\! He\left\{X^i - \Omega^i\right\}\! R^i + He\left\{ \smallpmat{N^i_1\\ N^i_2\\ N^i_3}\! \pmx{R N_{\nu x} & \Id - R & -\Id}\right\} \leq 0
\end{equation}
Then we have ${\xi^i}\tr X^i \xi^i \leq {\xi^i}\tr \Omega^i \xi^i$}
\end{lemma}

@@

\begin{figure*}
\begin{subequations}\label{eqn:LMI}
\begin{align}\label{eqn:lyapunov}
  &\Xi =\bmx{
  \begin{array}{c|c}
  \bmx{\bar{A}\tr\\
  \bar{B}\tr\\
  C\tr
  } P \bmx{\bar{A} & \bar{B} & C} - \bmx{
  P & 0 & 0\\
  0 & 0 & 0\\
  0 & 0 & 0
  } - (\1_l \otimes R_{\nu})\tr \He{\bX} (\1_l \otimes R_{\nu})
   + R_s\tr \bmx{
    S & Q\\
    \star & W
  }  R_s\hspace{.1em}& 0\\[1.5em]
\hline \\[-0.9em]
  0 & \hspace{.1em} 2 (\bR - \Id)
  \end{array}} < 0\\
  &\bmx{
    P & {Z_j^i}\tr\\
    \star & 2 \alpha T^i_{j,j} - \alpha^2 (\hat{\nu}_j^i)^{-2}
  } \geq 0 \ \forall i \in \left\{ 1, \dots, l \right\}, j \in \left\{ 1, \dots, n_{\phi_i} \right\} \label{eqn:inclusion}\\
  &{R^i}\tr\! He\left\{X^i - \Omega^i\right\} R^i + He\left\{ \pmx{N^i_1\\ N^i_2\\ N^i_3} \pmx{R N_{\nu x} & \Id - R & -\Id}\right\} \leq 0 \ \forall i \in \left\{ 1, \dots, l \right\} \label{eqn:finsler_constraint}\\
  &\bmx{P & {E_i}\tr \\ \star & \hat{\mu_i}^2} \geq 0 \forall i \in \left\{1, \dots, n_q \right\} \label{eqn:nonlin-inclusion-constraint}
\end{align}
\end{subequations}
\vspace{.5em}
\hrule
\end{figure*}
\begin{figure*}
\begin{equation}\label{eqn:first-step}
 \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}}\tr \left( \!
  \bmx{\bar{A}\tr\\
  \bar{B}\tr\\
  C\tr
  } P \bmx{\bar{A} & \bar{B} & C} - \bmx{
  P & 0 & 0\\
  0 & 0 & 0\\
  0 & 0 & 0
  } \right) \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}}
 - \pmx{\1_l \otimes \xi}\tr \bx \pmx{\1_l \otimes \xi}
 + \bmx{\tilde{x}\\ \tilde{\Phi}}\tr\! \bmx{S & Q\\ \star & W} \bmx{\tilde{x} \\ \tilde{\Phi}}
 + \sqrt{\boldsymbol{\eta}}\tr \He{\bR - \Id} \sqrt{\boldsymbol{\eta}}
\end{equation}
\vspace{.5em}
\hrule
\end{figure*}

@@

We can define the following definite-positive candidate Lyapunov function structured as: $V = \tilde{x}\tr P \tilde{x} + \He{\1_l\tr\!\boldsymbol{\eta}}$. 
By denoting $R_s$ as a proper transformation matrix such that $\bmx{\tilde{v}\tr & \tilde{\Phi}(Ex)}\tr = R_s \bmx{\tilde{x}\tr & \tilde{\psi}\tr & \tilde{\Phi}(Ex)}\tr$ then
\begin{equation}\label{eqn:sector-sign}
\bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}(Ex)}\tr R_s\tr \bmx{S & Q \\ \star & W} R_s \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}(Ex)} \geq 0\ \forall x \in \cE(P, x_*)
\end{equation}
With respect to \eqref{eqn:auxiliary} and \eqref{eqn:incremental} by denoting $\bmx{\tilde{x}\tr & \tilde{\psi}\tr & \tilde{\nu}\tr}\tr = R_{\nu} \bmx{\tilde{x}\tr & \tilde{\psi}\tr & \tilde{\Phi}(Ex)\tr}\tr$, if we pre and post multiply \eqref{eqn:lyapunov} by $\bmx{\tilde{x}\tr & \tilde{\psi}\tr & \tilde{\Phi}\tr & \sqrt{\boldsymbol{\eta}}\tr}\tr$ and its transpose\\

we obtain \eqref{eqn:first-step}. Considering \eqref{eqn:sector-sign} we verify Assumption \ref{ass:nonlin} then by collecting the proper terms and exploiting Kronecker product's properties we have
\begin{equation}
\begin{aligned}
&\bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}}\tr \left( \!
  \bmx{\bar{A}\tr\\
  \bar{B}\tr\\
  C\tr
  } P \bmx{\bar{A} & \bar{B} & C} - \bmx{
  P & 0 & 0\\
  0 & 0 & 0\\
  0 & 0 & 0
  } \right) \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}} + \\
  &+ \He{\1_l\tr (\bR - \Id) \boldsymbol{\eta}} - \mathbf{\Psi_x} < 0\\
\end{aligned}
\end{equation}
If all conditions in \eqref{eqn:LMI} are met then \eqref{eqn:lyapunov} implies the following:
\begin{equation}
    (\tilde{x}^+)^{\top} P \tilde{x}^+ - \tilde{x}\tr P \tilde{x} + \He{\1_l\tr (\boldsymbol{\eta}^+ - \boldsymbol{\eta})} = \Delta V < 0, 
\end{equation}
{\color{blue} for all $(x, \beta)\in \cE(P)$. Therefore, $\cE(P)$ is forward invariant and all trajectories starting inside such a set converge to $(x,0)$, thus concluding the proof.}
We conclude the proof by stating that $\forall (x, \boldsymbol{\eta}) \in \cE(P, x_*)$ the point $(x_*, \0)$ is LES, and $\Delta V(x, \boldsymbol{\eta}) < 0$, considering that the system is in Discrete Time (DT) then $\cE(P, x_*)$ is an invariant set and it is an inner-approximation of the ROA
\end{proof}
\subsection{Optimization procedure}

>>>>

\address[First]{University di Trento, Trento, Italy (e-mail: marco.sterlini@studenti.unitn.it) }
\address[Second]{LAAS-CNRS, Université de Toulouse, CNRS, Toulouse, France (e-mail:bu) }

@@

We can express now the new interdependency between the variables of interest:
\begin{equation}\label{eqn:incremental}
  \begin{aligned}
    \tilde{u} &= R_{\omega} \tilde{x} - N_{u \omega} R \tilde{\psi}\\
    \tilde{\nu} &= R N_{\nu x} \tilde{x} + (\Id - R) \tilde{\psi}
  \end{aligned}
\end{equation}

@@

\begin{lemma}\label{lem:finsler} \emph{Considering the triggering policy \eqref{eqn:dynamic_trig}, $R^i$ such that ${\xi^i}\tr = \!R^i \bmx{\tilde{x} & \tilde{\psi} & \tilde{\nu}}\tr\! = R^i \xi\tr$, with reference to the structure in \eqref{eqn:sec_cond} and assuming \eqref{eqn:incremental} holds for some $\underline{\xi}, \bar{\xi} \in \RR^{n_x + 2n_{\phi}}$ such that $\forall \xi \in \left[ \underline{\xi}, \bar{\xi}\right]$, if $\exists X^i \in\! \RR^{(nx + 2n_{\phi_i}) \times (nx + 2n_{\phi_i})},$ $N^i_1 \in \RR^{n_x \times n_{\phi_i}}, N^i_2, N^i_3 \in \RR^{n_{\phi_i} \times n_{\phi_i}}$ a diagonal matrix $T^i > 0 \in \RR^{n_{\phi_i} \times n_{\phi_i}}, G^i \in \RR^{n_{\phi_i} \times n_x}$ such that:
\begin{equation}\label{eqn:finsler}
     {R^i}\tr\! He\left\{X^i - \Omega^i\right\}\! R^i + He\left\{ \smallpmat{N^i_1\\ N^i_2\\ N^i_3}\! \pmx{R N_{\nu x} & \Id - R & -\Id}\right\} \leq 0
\end{equation}
Then we have ${\xi^i}\tr X^i \xi^i \leq {\xi^i}\tr \Omega^i \xi^i$}
\end{lemma}

@@

\begin{figure*}
\begin{subequations}\label{eqn:LMI}
\begin{align}\label{eqn:lyapunov}
  &\Xi =\bmx{
  \begin{array}{c|c}
  \bmx{\bar{A}\tr\\
  \bar{B}\tr\\
  C\tr
  } P \bmx{\bar{A} & \bar{B} & C} - \bmx{
  P & 0 & 0\\
  0 & 0 & 0\\
  0 & 0 & 0
  } - (\1_l \otimes R_{\nu})\tr \He{\bX} (\1_l \otimes R_{\nu})
   + R_s\tr \bmx{
    S & Q\\
    \star & W
  }  R_s\hspace{.1em}& 0\\[1.5em]
\hline \\[-0.9em]
  0 & \hspace{.1em} 2 (\bR - \Id)
  \end{array}} < 0\\
  &\bmx{
    P & {Z_j^i}\tr\\
    \star & 2 \alpha T^i_{j,j} - \alpha^2 (\hat{\nu}_j^i)^{-2}
  } \geq 0 \ \forall i \in \left\{ 1, \dots, l \right\}, j \in \left\{ 1, \dots, n_{\phi_i} \right\} \label{eqn:inclusion}\\
  &{R^i}\tr\! \He{X^i - \Omega^i} R^i + He\left\{ \pmx{N^i_1\\ N^i_2\\ N^i_3} \pmx{R N_{\nu x} & \Id - R & -\Id}\right\} \leq 0 \ \forall i \in \left\{ 1, \dots, l \right\} \label{eqn:finsler_constraint}\\
  &\bmx{P & {E_i}\tr \\ \star & \hat{\mu_i}^2} \geq 0 \forall i \in \left\{1, \dots, n_q \right\} \label{eqn:nonlin-inclusion-constraint}
\end{align}
\end{subequations}
\vspace{.5em}
\hrule
\end{figure*}
% \begin{figure*}
% \begin{equation}\label{eqn:first-step}
%  \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}}\tr \left( \!
%   \bmx{\bar{A}\tr\\
%   \bar{B}\tr\\
%   C\tr
%   } P \bmx{\bar{A} & \bar{B} & C} - \bmx{
%   P & 0 & 0\\
%   0 & 0 & 0\\
%   0 & 0 & 0
%   } \right) \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}}
%  - \pmx{\1_l \otimes \xi}\tr \He{\bX} \pmx{\1_l \otimes \xi}
%  + \bmx{\tilde{x}\\ \tilde{\Phi}}\tr\! \bmx{S & Q\\ \star & W} \bmx{\tilde{x} \\ \tilde{\Phi}}
%  + \sqrt{\boldsymbol{\eta}}\tr \He{\bR - \Id} \sqrt{\boldsymbol{\eta}}
% \end{equation}
% \vspace{.5em}
% \hrule
% \end{figure*}

@@

We can define the following definite-positive candidate Lyapunov function structured as: $V = \tilde{x}\tr P \tilde{x} + \He{\1_l\tr\!\boldsymbol{\eta}}$. 
By denoting $R_s$ as a proper transformation matrix such that $\bmx{\tilde{v}\tr & \tilde{\Phi}(Ex)}\tr = R_s \! \bmx{\tilde{x}\tr & \tilde{\psi}\tr & \tilde{\Phi}(Ex)}\tr$ then the following holds $\forall x \in \cE(P, x_*)$:
\begin{equation}\label{eqn:sector-sign}
\bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}(Ex)}\tr \! R_s\tr \! \bmx{S & Q \\ \star & W} R_s \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}(Ex)} \geq 0
\end{equation}
With respect to \eqref{eqn:auxiliary} and \eqref{eqn:incremental} by denoting \\$\xi = R_{\nu} \bmx{\tilde{x}\tr & \tilde{\psi}\tr & \tilde{\Phi}(Ex)\tr}\tr = R_{\nu} \zeta$, if we pre and post multiply \eqref{eqn:lyapunov} by $\bmx{\zeta\tr & \sqrt{\boldsymbol{\eta}}\tr}\tr$ and its transpose, by expressing the midterm as follows: 
\begin{equation}
\begin{aligned}
  &\zeta\tr \pmx{\1_l \otimes R_{\nu}}\tr \He{\bX} \pmx{\1_l \otimes R_{\nu}} \zeta = \\
  =& \pmx{\1_l 1 \otimes R_{\nu} \zeta}\tr \He{\bX} \pmx{\1_l 1 \otimes R_{\nu} \zeta} = \\
  =& \pmx{\1_l \otimes \xi}\tr \He{\bX} \pmx{\1_l \otimes \xi} = \\
  =& \1_l\tr \pmx{\Id_l \otimes \xi}\tr \He{\bX} \pmx{\1_l \otimes \xi} = \1_l\tr \mathbf{\Psi_x}
\end{aligned}
\end{equation}
and considering \eqref{eqn:sector-sign} we verify Assumption \ref{ass:nonlin} then by collecting the proper terms $\forall (x, \boldsymbol{\eta}) \in \cE(P, x_*)$ we have
\begin{equation}
\begin{aligned}
&\bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}}\tr \left( \!
  \bmx{\bar{A}\tr\\
  \bar{B}\tr\\
  C\tr
  } P \bmx{\bar{A} & \bar{B} & C} - \bmx{
  P & 0 & 0\\
  0 & 0 & 0\\
  0 & 0 & 0
  } \right) \bmx{\tilde{x} \\ \tilde{\psi} \\ \tilde{\Phi}} + \\
  &+ \He{\1_l\tr \bmx{(\bR - \Id) \boldsymbol{\eta} - \mathbf{\Psi_x}}} = \\
  &= (\tilde{x}^+)^{\top} P \tilde{x}^+ - \tilde{x}\tr P \tilde{x} + \He{\1_l\tr (\boldsymbol{\eta}^+ - \boldsymbol{\eta})} = \Delta V < 0, 
\end{aligned}
\end{equation}
{\color{blue} Therefore, $\cE(P, x_*)$ is forward invariant and all trajectories starting inside such a set converge to $(x, \0)$, thus concluding the proof.}
\end{proof}
\subsection{Optimization procedure}
